### 2019-12-17 tex/ms.tex
edits

\section{GFA Throughput Prediction}

@@

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{gfa_total_throughput}
    \caption{Total GFA throughput as a function of wavelength.}
    \label{fig:total_throughput}
\end{figure*}

@@

\section{Zeropoint Values Obtained}

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras. The zeropoints in terms of ADU are applicable to the raw data --- they do not have any flat fielding baked in. In all cases the zeropoints correspond to total light rather than signal within some nominal aperture. The median zeropoint in terms of e-/second is $r$ = 27.062 AB. This is slightly (3.4\%) deeper than the predicted zeropoint of $r$ = 27.026 AB for a source with total detected signal of 1 e-/second.

@@

Appended below is the full set of per-exposure, per-camera, per-amp scatter plots of GFA instrumental magnitudes versus PS1 $r$ band AB magnitudes for the set of exposures used during this study. The vertical yellow line indicates the magnitude threshold fainter than which GFA photometry was considered safe from potential saturation/nonlinearity. In each case the red line is fixed to have a slope of unity (the slope is not fit as a free parameter), and the y axis offset is set to the median of the difference between the PS1 AB magnitudes and the instrumental magnitudes for (sufficiently faint) matched sources.

% say what the vertical yellow line means...
% say what the red line means, emphasize that its slope is fixed to be exactly 1, not fit to match the data

>>>>

\section{GFA Throughput Prediction}
\label{sec:prediction}

@@

\begin{figure*}[ht]
        \includegraphics[width=7.0in]{gfa_total_throughput}
    \caption{Total GFA throughput as a function of wavelength. The data shown in this figure have been uploaded as a supplementary file.}
    \label{fig:total_throughput}
\end{figure*}

@@

\section{Measured Zeropoint Values}

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras. The values quoted in Table \ref{tab:zps} for each (camera, amp) pair are obtained by taking the median of the per-exposure zeropoint values derived for that (camera, amp) pair. The zeropoints in terms of ADU are applicable to the raw data --- they do not have any flat fielding baked in. In all cases the zeropoints are meant to correspond to total light rather than signal within some nominal aperture. The median zeropoint in terms of e-/second is $r$ = 27.062 AB. This is slightly (3.4\%) deeper than the predicted zeropoint ($\S$\ref{sec:prediction}) of $r$ = 27.026 AB for a source with total detected signal of 1 e-/second.

@@

Appended below is the full set of per-exposure, per-camera, per-amp scatter plots of GFA instrumental magnitudes versus PS1 $r$ band AB magnitudes for the set of exposures used during this study. The vertical yellow line indicates the magnitude threshold fainter than which GFA photometry was considered safe from potential saturation/nonlinearity. In each case the red line is fixed to have a slope of unity (the slope is not fit as a free parameter), and its y axis offset is the median of the difference between the GFA instrumental magnitudes and the PS1 AB magnitudes for (sufficiently faint) matched sources.
